Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-25 cav2017/cav2017.tex
Updated experimental description.
Updated discusison of experimental results, confirming our research
questions.

All benchmarks were discretized with different sample times using 
the approach described in the Appendix~\ref{sec:appendix}. 
All experiments were performed considering $\underline{x_{i}}=-1$ and 
$\overline{x_{i}}=1$ and the inputs $u_{k}=0, \forall k>0$.
We have conducted the experimental evaluation on a 12-core 2.40 GHz
Intel Xeon E5-2440 with 96 GB of RAM and Linux OS.

\textcolor{red}{Pascal, Can you please describe our we measure time?
All times given are wall clock time in seconds as measured by the UNIX date command.}

\textcolor{red}{Pascal, can you please describe the timeout?}

@@

We give the run-times required to synthesize a stable controller for each
benchmark in Table~\ref{tab:results}.  
Here \textit{Benchmark} is the name of the employed
benchmark, $\mathcal{F}_{\langle I_p,F_p \rangle}$ is the fixed-point precision used to model the plant, while \textit{Time}
is the total time (in seconds) required to synthesize a stable controller
for the given plant, for approach 1 and approach 2. The precision for the controller, $\mathcal{F}_{\langle I_c,F_c \rangle}$, is always chosen to be $I_c = 8, F_c = 8$.

For the majority of our benchmarks, the conjecture stands that the Acceleration back-end is faster than the basic multi-staged verification approach. However, it does fail to find solutions to XXX benchmarks, where the numbers given in the discretization matrices are really small.

The basic multi-staged verification approach finds X / X benchmarks, albeit in an expected slower time. The solutions that are not found are due to time-out or XXXX

\begin{table}
\centering
\begin{tabular}{| r | c | c | r | c | r |}
\hline
\# & Benchmark  & \multicolumn{2}{|c|}{Multi-stage}                 & \multicolumn{2}{|c|}{Abstraction} \\
   &            & $\mathcal{F}_{\langle I_p,F_p \rangle}$ & Runtime & $\mathcal{F}_{\langle I_p,F_p \rangle}$ & Runtime \\\hline
1  & Cruise Control      & 8,16   & 6875   & 16,16  & 241    \\
2  & DC Motor            & 8,16   & 8103   & 20,20  & 5376   \\
3  & Helicopter          & \xmark & \xmark & 16,16  & 2120   \\
4  & Inverted Pendulum   & 8,16   & 7813   & 16,16  & 387    \\
5  & Magnetic Pointer    & \xmark & \xmark & 28,28  & 132845 \\
6  & Magnetic Suspension & 12,20  & 8727   & 32,32  & 7854   \\
7  & Pendulum            & 8,16   & 9008   & 20,20  & 1150   \\
8  & Suspension          & 12,20  & 49410  & \xmark & \xmark \\
9  & Tape Driver         & 8,16   & 9177   & \xmark & \xmark \\
10 & Satellite           & 8,16   & 8975   & \xmark & \xmark \\\hline

\end{tabular}
\caption{Experimental results \label{tab:results}}
\end{table}

he median runtime for our benchmark set is XXXX.  Overall,
the average synthesis time amounts to approximately XXX minutes.  We
consider these times short enough to be of practical use to control
engineers, and thus affirm RQ1.

>>>>

All benchmarks were discretized with different sample times using 
the approach described in the Appendix~\ref{sec:appendix}. 
All experiments were performed considering $\underline{x_{i}}=-1$ and 
$\overline{x_{i}}=1$ and the inputs $u_{k}=0, \forall k>0$.
We have conducted the experimental evaluation on a 12-core 2.40 GHz
Intel Xeon E5-2440 with 96 GB of RAM and Linux OS. We used the Linux \emph{times} command
to measure CPU time used for each benchmark. The experimental runtime was limited to
one hour per benchmark.

@@

We give the run-times required to synthesize a stable controller for each
benchmark in Table~\ref{tab:results}.  
Here \textit{Benchmark} is the name of the employed
benchmark, $\mathcal{F}_{\langle I_p,F_p \rangle}$ is the fixed-point precision used
to model the plant, while \textit{Time}
is the total time (in milliseconds) required to synthesize a stable controller
for the given plant, for CEGIS with multi-staged verification as well as
abstraction-based CEGIS. The precision for the controller,
$\mathcal{F}_{\langle I_c,F_c \rangle}$, is always chosen to be $I_c = 8, F_c = 8$.

For the majority of our benchmarks, the conjecture stands that the abstraction-based back-end
is faster than the basic multi-staged verification approach. However, it does fail to
find solutions to 3 benchmarks, as compared to 2 with the multi-staged back-end, where
the numbers given in the discretization matrices are too small. In direct comparison the
abstraction-based is able to find a solution in approximately 35\% of the time required
using the multi-staged back-end. The two back-ends complement each other well in their
benchmark coverage and together solve all benchmarks provided in the set.

\begin{table}
\centering
\begin{tabular}{| r | c | c | r | c | r |}
\hline
\# & Benchmark  & \multicolumn{2}{|c|}{Multi-staged}                 & \multicolumn{2}{|c|}{Abstraction} \\
   &            & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} \\\hline
1  & Cruise Control      & 8,16   & 6875   & 16,16  & 241    \\
2  & DC Motor            & 8,16   & 8103   & 20,20  & 5376   \\
3  & Helicopter          & \xmark & \xmark & 16,16  & 2120   \\
4  & Inverted Pendulum   & 8,16   & 7813   & 16,16  & 387    \\
5  & Magnetic Pointer    & \xmark & \xmark & 28,28  & 132845 \\
6  & Magnetic Suspension & 12,20  & 8727   & 32,32  & 7854   \\
7  & Pendulum            & 8,16   & 9008   & 20,20  & 1150   \\
8  & Suspension          & 12,20  & 49410  & \xmark & \xmark \\
9  & Tape Driver         & 8,16   & 9177   & \xmark & \xmark \\
10 & Satellite           & 8,16   & 8975   & \xmark & \xmark \\\hline

\end{tabular}
\caption{Experimental results with runtime in milliseconds \label{tab:results}}
\end{table}

The median runtime for our benchmark set is 7.9\,s.  Overall,
the average synthesis time amounts to approximately 17.2\,s.  We
consider these times short enough to be of practical use to control
engineers, and thus affirm RQ1.
